Memory-aware Adaptive Scheduling of Scientific Workflows on Heterogeneous Architectures\\

### 2025-03-11 main.tex
moved paragraph in Sec. IV-A, some minor fixes

@@

\new{Due to a varying nature of the workflow generator, some workflows can have smaller makespans than their
smaller counterparts due to more parallelism at nodes with higher out-degree or other factors of the workflow's
internal composition.}

@@

Thus, the scheduler receives deviation values and makes decision based on them\new{, hence
leading to an execution mode  \textit{with recomputation}.}
This leads to several types of possible issues:
%
\begin{itemize}
\item 
  A processor is blocked by another task. If the scheduler underestimated the execution time of a task,
  it will block another one from starting.
\item 
  A predecessor has not finished yet.
  The scheduler may request a task to start on its processor, while
  some of the predecessors of the task have in fact not yet completed their execution -- 
  the task is therefore not yet ready.
%        A similar situation, but a task could start on its processor, but one or more of its parents a
%        are not ready yet.
\item 
  Not enough memory. If the scheduler underestimated the amount of memory a task requires, this task might not be able to execute on a chosen processor.
\item 
  A task took less time than expected. We only consider this case if a task took more than 10\% less
  time than expected. In this case, we want to exploit the newly acquired free time by possibly starting other tasks earlier.
\end{itemize}

>>>>

\new{Note that, due to a varying nature of the workflow generator, some workflows can have smaller makespans than their
smaller counterparts due to more parallelism at nodes with higher out-degree or other factors of the workflow's
internal composition.}

@@

@@

Thus, the scheduler receives deviation values and makes decisions based on them\new{, which
leads to an execution mode  \textit{with recomputation}.}
This mode leads to several types of possible issues:
%
\begin{itemize}
\item 
  A processor is blocked by another task. If the scheduler underestimated the execution time of a task,
  it will block another one from starting.
\item 
  A predecessor has not finished yet.
  The scheduler may request a task to start on its processor, while
  some of the predecessors of the task have in fact not yet completed their execution -- 
  the task is therefore not yet ready.
%        A similar situation, but a task could start on its processor, but one or more of its parents a
%        are not ready yet.
\item 
  Not enough memory. If the scheduler underestimated the amount of memory a task requires, this task might not be able to execute on a chosen processor.
\item 
  A task took less time than expected. We only consider this case if a task took more than 10\% less
  time than expected. In this case, we want to exploit the newly acquired free time by possibly starting other tasks earlier.
\end{itemize}
